WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-06-02 ms.tex
Add some figures

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{crlb_tau}
    \end{center}
    \caption{\label{fig:crlb-tau}\ac{CRLB} on root\nobreakdashes-mean square timing uncertainty, using the likelihood for the full GW data (Equation~\ref{eq:gaussian-likelihood-spa}; dashed diagonal line) or the autocorrelation likelihood (Equation~\ref{eq:autocor-likelihood}; solid lines) with a selection of arrival time priors.}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{fishfactor}
    \end{center}
    \caption{\label{fig:fishfactor}Ratio between Fisher matrix elements (solid: $\mathcal{I}_{\gamma\gamma}$, dashed: $\mathcal{I}_{\gamma\tau}$, dotted: $\mathcal{I}_{\tau\tau}$) for the the autocorrelation likelihood and the full GW data. Colors correspond to different arrival time priors as in Figure~\ref{fig:crlb-tau}.}
\end{figure}
